---
output: 
  word_document:
    reference_docx: ArmyMemoTemplate_Sample.docx
---

```{r setup, include=FALSE}
# This was built with help from:
# MAJ John Case, he's awesome.
# https://rmarkdown.rstudio.com/articles_docx.html 
# https://www.markdownguide.org/basic-syntax/
# https://rapporter.github.io/pander/
# https://www.rdocumentation.org/packages/pander/versions/0.6.3

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.align = 'center', fig.height = 3.5, fig.width = 6)
```

\newline <!--Don't delete this--> 
<!--This is a really annoying and hacky way to get the office symbol and date aligned well--> 
<!--Just change your office symbol and date to the appropriate ones see below--> 
<!--Don't change the pipes, this is building a table-->

||| 
|:---|---:| 
|MyOfficeSymbol | &nbsp; `r format(Sys.Date(), '%d %b %y')`|
|&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; |&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp;  |

\newline

MEMORANDUM FOR `r stateData$State`

\newline

SUBJECT: State Murders Compared to National Numbers

\newline

\newline

# This is a report that shows how `r stateData$State` compares to the rest of the nation in murders for 1973.

# **Murders.**  `r stateData$State` had `r as.character(stateData$Murder)` murder(s) in 1973.  One can see how this compares to the nation in Figure 1 below.

```{r murderDistro, echo = FALSE, fig.cap='Relative Murders for 1973', fig.width=6.5}
p + ggplot2::geom_vline(xintercept = stateData$Murder)
```

`r ifelse(stateData$Murder > nationalMean, 'Clearly we have work to do boss.', 'We are doing well.')`

\newline

\newline

\newline

\newline

\newline

# The point of contact for this is the undersigned at 867-5309.

\newline

\newline

||||
|:---|:---|
|1 Encls | FIRST MI LAST|
|1. Enclosure 1 | RANK, BRANCH |
| | Job |
| ||
|&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; |&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; |
